---
title: "FIN450 Final Assignment"
output: html_document
date: "2023-11-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Potential Ideas:

Job Market Analysis
Hotel Booking Cancellation Prediction
Movie Revenue Generation
Video Game Trends and Sales
Disease Outbreak Prediction

Crime Incidents Across Canada (USA?)

- Web scrape all crime reports from the past 10 years 
- Import data into dfs
- Analyse data based on underlying influence (Interest Rates, Weather, Housing Prices, Lunar Phases, proximity of fast food restraints, trees, government in power, number of social programs)
- Build a report that discusses the influence of these factors, which ones are the most prominent, and our proposed solution.


```{r Libraries}
library(tidyverse)
library(RSelenium)
library(netstat)
library(jsonlite)
library(robotstxt)
library(rvest)

```

```{r remDr Start}
# Start the server
rs_driver_object <- rsDriver(browser = "firefox",
                             chromever = NULL,
                             verbose = FALSE
                             )

# Create a Client object
remDr <- rs_driver_object$client
```
 
```{r imdb Scraping WIP}

# Website to navigate
website <- 'https://www.imdb.com/search/title/'

# Open a browser
remDr$open()

# Navigate to website
remDr$navigate(website)

titletype <- remDr$findElement(using = "id", value = "titleTypeAccordion")$clickElement()

movie_filter_button <- remDr$findElement(using = "xpath", value = "//button[contains(@data-testid, 'test-chip-id-movie')]")$clickElement()

awards <- remDr$findElement(using = "id", value = "awardsAccordion")$clickElement()

top_1000_button <- remDr$findElement(using = "xpath", value = "//button[contains(@data-testid, 'test-chip-id-top-1000')]")$clickElement()

results_button <- remDr$findElement(using = "xpath", value = "//button[contains(@data-testid, 'adv-search-get-results')]")$clickElement()

# Click the "See more info" button for all movies
info_buttons <- remDr$findElements(using = "xpath", value = "//button[contains(@class, 'ipc-icon-button') and contains(@class, 'dli-info-icon')]")
for (button in info_buttons) {
  button$clickElement()
  

  Sys.sleep(2)
  
  # Close the info tab
  close_button <- remDr$findElement(using = "xpath", value = "//div[contains(@class, 'ipc-promptable-base__close')]//button[@title='Close Prompt']")
  close_button$clickElement()
}


```

```{r Revenue For the top 1000 movies}
website <- 'https://www.boxofficemojo.com/'
remDr$open()
remDr$navigate(website)
alltime <- remDr$findElement(using = 'link text', 'All Time (Worldwide)')$clickElement()


scrape_movie_data <- function(num_pages = 5) {
  all_data <- list()  # Initialize an empty list to store the collected data

  for (page in 1:(num_pages - 1)) {
    # Read the HTML of the current page
    url <- as.character(remDr$getCurrentUrl())
    webpage <- read_html(url)
    
    # Extract the table data 
    table_data <- webpage %>% 
      html_nodes("#table table") %>% 
      html_table(fill = TRUE)
    
    # Add the data to the overall list
    all_data <- c(all_data, list(table_data))
    
    # Click the "Next" button
    next_button <- remDr$findElement(using = 'css selector', '.a-last a')$clickElement()
  }

  # Collect data from the last page
  url <- as.character(remDr$getCurrentUrl())
  webpage <- read_html(url)
  table_data <- webpage %>% 
    html_nodes("#table table") %>% 
    html_table(fill = TRUE)
  all_data <- c(all_data, list(table_data)) 

  return(all_data)
}

result_data <- scrape_movie_data(num_pages = 5)

last_page <- result_data[[5]]
last_page[[1]]$Rank <- as.integer(gsub(",", "", last_page[[1]]$Rank))
result_data[[5]] <- last_page

rev_df <- bind_rows(result_data)

rev_df


```

```{r}
click_movie_links <- function(movie_titles) {
  for (title in movie_titles) {
    # Find and click the link for the current movie title
    movie_link <- remDr$findElement(using = 'link text', title)$clickElement()
    
    remDr$goBack()
    
    # Pause
    Sys.sleep(1)
  }
}

movie_titles <- rev_df$Title
movies_per_page <- 200

# Iterate through each page
for (page in seq(1, nrow(rev_df), movies_per_page)) {
  # Extract movie titles for the current page
  current_page_titles <- movie_titles[page:(page + movies_per_page - 1)]
  
  # Click the embedded link for each movie title and go back
  click_movie_links(current_page_titles)
  
  # Click the next page link
  remDr$findElement(using = 'css selector', '.a-last a')$clickElement()
  
  # Pause
  Sys.sleep(1)
}

```

```{r imdb scraping release}

library(rvest)
library(stringr)

# Replace 'your_url_here' with the actual URL of the webpage
url <- "https://www.imdb.com/calendar/?ref_=rlm&region=US&type=MOVIE"

# Read the HTML content of the webpage
webpage <- read_html(url)

# Use the identified CSS selector for the movie elements
movie_elements <- html_nodes(webpage, '.ipc-metadata-list-summary-item')

# Extract information from each movie element
movies_data <- lapply(movie_elements, function(movie) {
  # Extract title
  title <- html_text(html_node(movie, '.ipc-metadata-list-summary-item__t'))

  # Extract year (assuming it's within the title link)
  year <- gsub("[^0-9]", "", str_match(title, "\\((\\d{4})\\)")[, 2])

  # Extract genres
  genres <- html_text(html_nodes(movie, '.ipc-inline-list--show-dividers.ipc-metadata-list-summary-item__tl .ipc-inline-list__item'))

  # Extract stars
  stars <- html_text(html_nodes(movie, '.ipc-inline-list--show-dividers.ipc-metadata-list-summary-item__stl .ipc-inline-list__item'))

  # Extract director (assuming it's within an element with a specific class)
  director <- html_text(html_node(movie, '.your-director-selector-here'))

  # Return a list with the extracted information
  list(title = title, year = year, genres = genres, stars = stars, director = director)
})

movies_df <- do.call(rbind, movies_data)

# Print the resulting data frame
print(movies_df)

```

